---
title: "White Fragility & Moral Affirmation S3"
format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
---



# Main Analyses (Moral Fragility Model)

## **Systemic Racism as a Moral Threat**

### **Defensiveness and Systemic Racism**

```{r Defensiveness across conditions}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_defensive_reverse = mean(defensive_reverse, na.rm = TRUE))
summary(lm(defensive_reverse ~ article_condition, wf_dt2))
```

#### The wealth gap article is not associated with increased defensiveness.  

### **Affect and Systemic Racism**

#### The wealth gap article, lead to the most sadness. 

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_sad = mean(BMIS_sad_2, na.rm = TRUE))
summary(lm(BMIS_sad_2_Z ~ article_condition, wf_dt2))
```

#### The no gap condition was the most optimistic, while the gap condition was more pessimistic than the control condition.

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_tone = mean(article_tone, na.rm = TRUE))
summary(lm(article_tone_Z ~ article_condition, wf_dt2))
```

#### The gap condition had the most negative tone, while the no gap condition had the most positive tone. 

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_sentiment = mean(article_sentiment, na.rm = TRUE))
  summary(lm(article_sentiment_Z ~ article_condition, wf_dt2))
```

#### People felt worse after reading the gap article, and they felt the best after reading the no gap article. 

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_feel = mean(article_feel, na.rm = TRUE))
  summary(lm(article_feel_Z ~ article_condition, wf_dt2))
```

#### The gap condition lead to the most shame, while the nogap and control condition lead to similar amounts of shame.

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_shame = mean(BMIS_shame_2, na.rm = TRUE))
summary(lm(BMIS_shame_2_Z ~ article_condition, wf_dt2))
```

#### The gap condition lead to the most guilt, while the nogap and control condition lead to similar amounts of guilt.

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_guilt = mean(BMIS_guilt_2, na.rm = TRUE))
summary(lm(BMIS_guilt_2_Z ~ article_condition, wf_dt2))
```

#### The gap condition lead to the most outrage, while the nogap and control condition lead to similar amounts of outrage.

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_outraged = mean(BMIS_outraged_2, na.rm = TRUE))
  summary(lm(BMIS_outraged_2_Z ~ article_condition, wf_dt2))
```

#### People were no more or less empathetic in the gap condition.

```{r}
wf_dt2 %>%
  group_by(article_condition) %>%
  summarize(mean_empathetic = mean(BMIS_empathetic_2, na.rm = TRUE))
summary(lm(BMIS_empathetic_2_Z ~ article_condition, wf_dt2))
```
