---
title: "White Fragility & Moral Affirmation S3"
format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
---

# Personal Self-Esteem after reading article
## Affect
```{r}
summary(lm(SE_1_Z ~ BMIS_angry_1_Z, wf_dt2))
summary(lm(SE_1_Z ~ BMIS_shame_1_Z, wf_dt2))
summary(lm(SE_1_Z ~ BMIS_guilt_1_Z, wf_dt2))
summary(lm(SE_1_Z ~ BMIS_outraged_1_Z, wf_dt2))
summary(lm(SE_1_Z ~ article_tone_Z, wf_dt2))
summary(lm(SE_1_Z ~ article_feel_Z, wf_dt2))
summary(lm(SE_1_Z ~ article_sentiment_Z, wf_dt2))
summary(lm(SE_1_Z ~ defensive_reverse_Z, wf_dt2))
summary(lm(SE_1_Z ~ defensive_reverse_Z + BMIS_angry_1_Z + BMIS_shame_1_Z + BMIS_outraged_1_Z + BMIS_sad_1_Z, wf_dt2))
```

#### Negative Affect (anger, shame, guilt, outrage, article tone/feelings; B = -.15 to -.25) is related to lower personal self-esteem, so is defensiveness and it is very robust as the effect holds even when controlling for all of the variables. 

# Public Collective Self-Esteem after reading article
## Affect
```{r}
summary(lm(public_CSE1_Z ~ BMIS_angry_1_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ BMIS_shame_1_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ BMIS_guilt_1_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ BMIS_outraged_1_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ article_tone_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ article_feel_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ article_sentiment_Z, wf_dt2))
summary(lm(public_CSE1_Z ~ article_condition, wf_dt2))
summary(lm(public_CSE1_Z ~ defensive_reverse_Z + BMIS_angry_1_Z + BMIS_shame_1_Z + BMIS_outraged_1_Z + BMIS_sad_1_Z, wf_dt2))
```

#### Negative Affect (anger, shame, guilt, outrage, article tone/feelings; B = -.15 to -.29) is related to lower public collective self-esteem (if you think others have a postive image of White Americans), so is defensiveness and it is very robust as the effect holds even when controlling for all of the variables. 


# Private Collective Self-Esteem after reading article
## Affect
```{r}
summary(lm(private_CSE1_Z ~ BMIS_angry_1_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ BMIS_shame_1_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ BMIS_guilt_1_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ BMIS_outraged_1_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ article_tone_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ article_feel_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ article_sentiment_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ defensive_reverse_Z, wf_dt2))
summary(lm(private_CSE1_Z ~ defensive_reverse_Z + BMIS_angry_1_Z + BMIS_shame_1_Z + BMIS_outraged_1_Z + BMIS_sad_1_Z, wf_dt2))
```

#### Negative Affect (anger, shame, guilt, outrage, article tone/feelings; B = -.15 to -.25) is related to lower private collective self-esteem (personal self-esteem regarding White Americans), but not defensiveness. 
